%% ------------------------------------------------------------------------
%% Copyright (C) 2023 Log Creative <logcreative@outlook.com>
%%
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%   http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2005/12/01 or later.
%%
%% This work has the LPPL maintenance status `maintained'.
%% 
%% The Current Maintainer of this work is Log Creative.
%% ------------------------------------------------------------------------

\documentclass[full]{l3doc}
\EnableCrossrefs
\CodelineIndex
\RecordChanges
\SetupDoc{reportchangedates}

\NewDocumentCommand{\presenter}{}{\textsc{Presenter}}
\title{\presenter: A \LaTeX{} presentation class with seamless migration}
\author{Log Creative}
\date{2023-01-30 \quad v0.0.6}

\begin{document}

\maketitle

\begin{abstract}
  \presenter{} is a \LaTeX{} document class adapted to regular \LaTeX{}
  syntaxes and designed for making minimalist presentations, written in
  \LaTeX3 and \pkg{l3draw}.
\end{abstract}

\tableofcontents

\begin{documentation}

  \section{Philosophy}

  \subsection{Seamless Migration}

  Users should feel seamless on migrating from document class like \cls{article},
  \cls{report}, \cls{book} to \cls{presenter} without modifying many structures.

  \subsection{Stay On Top}

  Sectioning information will stay on the top of the slides.

  \subsection{Minimal Design}

  The minimal design is for catering to the current trend without introducing
  too many complexities.

  \section{Related Works}

  \begin{description}
    \item[\href{https://github.com/josephwright/beamer}{\cls{beamer}}]

      One of the most popular presentation document classes in the current
      \LaTeX{} world.

    \item[\href{https://github.com/Liam0205/easy_slides}{\pkg{easy-slides}}]

      Entirely based on \cls{article} class, to create presentations.

    \item[\href{https://github.com/LogCreative/AutoBeamer}{\pkg{AutoBeamer}}]

      Origin of the idea. Provides a package to redefine some sectioning commands
      for basic translation from \cls{article} class to \cls{beamer} class.
      Provides a web page to convert Markdown document to \cls{beamer} class code.

  \end{description}

\end{documentation}

\begin{implementation}

  \section{Implementation}

  \DocInput{presenter.dtx}

\end{implementation}

\PrintChanges

\PrintIndex

\end{document}